---
title: "Week 3 - TRasportation Vis"
output: html_notebook
---
### Loading the packages

```{r}
library(tidyverse)
library(nycflights13)
```


### Exploring the data set {.tabset}

The package *nycflights13* has the data of several airports, flights and planes. Below some examples of the data available with such packages:


```{r}
airlines
```

```{r}
airports
```

```{r}
planes
```


```{r}
flights
```

#### Visualizing the department delay of the airports

**getting the data**

```{r}
dep_delay <- flights %>% select(origin, dep_time, sched_dep_time) %>% mutate(delay = dep_time - sched_dep_time)

dep_delay
```

**filtering the top five delayers**

```{r}
dep_delay_late <- filter(dep_delay, delay > 0)
```

```{r}
delay_summary <- dep_delay_late %>% group_by(origin) %>% summarise(count = n())
```
```{r}
delay_summary
```

```{r}
delay_summary$type <- "delayed"
```



**getting all flights**


```{r}
not_delay_summary <- dep_delay %>% group_by(origin) %>% summarise(count = n())
```

```{r}
not_delay_summary
```
```{r}
not_delay_summary$type <- "all"
```

**final data set**


```{r}
final_delay_all <- rbind(delay_summary, not_delay_summary)
```

```{r}
final_delay_all
```

**Creating the GGPlot**

```{r}


plot1 <- ggplot(data = final_delay_all, mapping = aes(x = factor(origin),
                                             y = count)) +
  geom_col(mapping = aes(fill = factor(type)), position = "dodge") +
  geom_text(mapping = aes(fill = factor(type), label =count),
            vjust=-0.35,
            position = position_dodge(width = 0.9)) +
  scale_fill_grey(start = 0.2, end = 1) +
  theme(panel.background = element_rect(fill = "lightsteelblue1"),
        plot.background = element_rect(fill = "lightskyblue3"),
        legend.background = element_rect(fill = "lightskyblue3", colour = "black"),
        panel.grid = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_line( size=.25, color="black" ),
        plot.title = element_text(hjust = 0.5, size = 20, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5, size = 16),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14)) +
  labs(title = "New York Flights (2013) ✈",
       subtitle = "All Flights vs. Delayed Flights",
       y = "Number of Flights",
       x = "Airport",
       caption = "Source: nycflights13")

plot1
```
**transforming it into plotly**

```{r}
ggsave(plot = plot1, width = 12, height = 8, filename = "delayed_flights.png")
```

```{r}
ggplotly(plot1)
```


#### Visualizing the carriers

**getting the data**

```{r}
flights
```


```{r}
carriers <- flights %>% group_by(carrier) %>% summarise(count = n())
carriers
```


**Visualization**


```{r}
plot2 <- ggplot(data = carriers, mapping = aes(x = factor(carrier),
                                             y = count)) +
  geom_col(mapping = aes(fill = carrier)) +
  geom_text(mapping = aes(label = count),
            vjust=-0.35,
            position = position_dodge(width = 0.9)) +
  theme(panel.background = element_rect(fill = "lightsteelblue1"),
        plot.background = element_rect(fill = "lightskyblue3"),
        legend.background = element_rect(fill = "lightskyblue3", colour = "black"),
        panel.grid = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_line( size=.25, color="black" ),
        plot.title = element_text(hjust = 0.5, size = 20, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5, size = 16),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14)) +
  labs(title = "New York Flights (2013) ✈",
       subtitle = "All Flights vs. Delayed Flights",
       y = "Number of Flights",
       x = "Carrier",
       caption = "Source: nycflights13")

plot2
```

```{r}
ggsave(plot = plot2, width = 12, height = 8, filename = "carrier_flights.png")
```




#### Most Common destinations
